---
title: "Hotels in Vienna Analysis"
author: "Maeva_Braeckevelt"
date: "20/12/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, include=F, message=FALSE, echo=FALSE, eval=TRUE}
# Packages to use
library(tidyverse)
require(scales)
library(lspline)
library(estimatr)
library(texreg)
library(ggthemes)
library(tidyverse)
library(geosphere)
library(moments)
library(dplyr)
library(knitr)
library(pander)
library(jtools)
library(huxtable)

# First, I will import ly clean data from github
my_url <- "https://raw.githubusercontent.com/Maeva2408/DA2_Extra_exercices/main/Exercice_2_chap7/Data/Clean/hotel_vienna.csv"
Vienna <- read_csv( my_url )
```

# Introduction

This analysis aimed at analyzing the pattern of association between the price of the hotels in Vienna and the ratings. The data used was gathered in a csv files : The hotelbookingdata.csv. It was download from a comparison website and it was anonymized and slightly altered to ensure confidentiality.The main variables that I used were: the price in dollars (y) and the number of stars (x). My sample is the price of the hotels in Vienna in the weekday of November 2017.


# Non-parametric regression
## Bin scatter with four bins & Lowess regression
```{r, echo=FALSE, out.width = "70%",fig.align='center',results='asis', message=FALSE}
scatter_vienna <- ggplot(  Vienna , aes(x = ratings, y = price )) +
  geom_point(fill= "orangered4", col= "salmon"  )+
  theme_bw()+
  scale_fill_wsj()+
  labs(x='Number of stars',y='Price ($)')

scatter_vienna + geom_smooth(method=loess,se=F,formula='y~x',color='black')

```

I observed that there is a positive slope in general. More stars the hotels have, more expensive are the hotels. If I look at the hotel with the worse rating and one with one of the best ratings, the price is around the double. So, I did uncover a pattern of association but I don't have any interpretable quantitave answer. I will do a simple linear regression.

### Simple Linear regression (A5)
```{r, echo=FALSE, out.width = "70%",fig.align='center',results='asis', message=FALSE}

## Simple Linear regression
reg1 <- lm_robust( price ~ ratings , data = Vienna , se_type = "HC2" )

## Vizualition
ggplot( data = Vienna, aes( x = ratings, y = price ) ) + 
  geom_point( color='salmon') +
  theme_bw()+
  geom_smooth( method = lm , color = 'orangered4' )+
  labs(x = "number if stars",y = "price in $") 

```
This graph represents the simple linear regression between the price of hotels in Vienna and the number of price.

**Formula :  Price = -76,16 + 46,07 * stars **

**Alpha** : -76,16 not a meaningful interpretation

**Beta** : the hotels that have 1 more stars are, on average, 46,07$ more expensive

However my R square is 19%, so only 19% of variation of the price is captured in this regression.

```{r, message = FALSE, echo=FALSE,warning=FALSE, size=1, fig.height=4, out.width = "50%"}
df_vienna_stat <- export_summs(reg1,
                               model.names = c( "Linear"),
                               caption= "model summary statistics")
as_hux(df_vienna_stat)
```


